### 2012-11-25 paper.tex
comparisons

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &  Correctly classified\\
	\midrule
	Decision Tree		\\
  Random Forest		\\
  Naive Bayes			&0.897  		& 0.244   	& 0.958   & 0.897  &0.92      	& \\
  SVM							&0.959     	&0.959     	&0.919   	&0.959   &0.939     	&	0.959\\
  kNN							&0.959     	&0.959     	&0.919   	&0.959   &0.939     	&	0.959\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the echocardiogram dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &  Correctly classified\\
	\midrule
	Decision Tree		& 0.86    	& 0.307   	& 0.854   & 0.86   & 0.855     & 		& FEHLT\\
  Random Forest		& 0.859   	& 0.333   	& 0.853   & 0.859  & 0.851     	& FEHLT\\
  Naive Bayes		 	& 0.83    	& 0.186   	& 0.854   & 0.83   & 0.837     	& FEHLT\\
  SVM							& 0.849    	& 0.343     &0.842   	&0.849   &0.842     	& 0.849\\
  kNN							&0.835     	&0.331      &0.829    &0.835   &0.831				& 0.835\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the adult dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &  Correctly classified\\
	\midrule
	Decision Tree 	&  0.558   & 0.243   & 0.557     	& 0.558  & 0.557     & FEHLT\\
  Random Forest		&  0.556   & 0.241   & 0.562     	& 0.556  & 0.556     & FEHLT\\
  Naive Bayes		 	&  0.508   & 0.243   & 0.528     	& 0.508  & 0.513     & FEHLT\\
  SVM							& 0.849    & 0.343   &0.842   		& 0.849  & 0.842 		 & 0.492\\
  kNN							&0.489     &0.284    &0.487     	& 0.489  & 0.488 		 & 0.489\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the contraceptive method choice dataset}
\end{table}
\bibliography{references}

>>>>

\tableofcontents

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &  Correctly classified\\
	\midrule
	Decision Tree		\\
  Random Forest		\\
  Naive Bayes			&   0.897  & 0.244   & 0.958     & 0.897  & 0.92     \\
  SVM							&0.959     	&0.959     	&0.919   	&0.959   &0.939     	&	0.959\\
  kNN							&0.959     	&0.959     	&0.919   	&0.959   &0.939     	&	0.959\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the echocardiogram dataset}
\end{table}

%% 
%%
\begin{table*}[htb]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
              &  TP Rate & FP Rate & Precision & Recall & F-Measure & Class    \\  \midrule
              &   0.75   & 0.097   & 0.25      & 0.75   & 0.375     & 0 \\
              &   0.903  & 0.25    & 0.988     & 0.903  & 0.944     & 1 \\
Weighted Avg. &   0.897  & 0.244   & 0.958     & 0.897  & 0.92      &   \\ \bottomrule
  \end{tabular*}
\caption{Echocardiogram -- Naive Bayes with SMOTE filter} 
\label{tab:echo:bayes:2d}
\end{table*}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &  Correctly classified\\
	\midrule
	Decision Tree		& 0.86    	& 0.307   	& 0.854   & 0.86   & 0.855     & 		& FEHLT\\
  Random Forest		& 0.859   	& 0.333   	& 0.853   & 0.859  & 0.851     	& FEHLT\\
  Naive Bayes		 	&  0.83    & 0.186   & 0.854     & 0.83   & 0.837     \\
  SVM							& 0.849    	& 0.343     &0.842   	&0.849   &0.842     	& 0.849\\
  kNN							&0.835     	&0.331      &0.829    &0.835   &0.831				& 0.835\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the adult dataset}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &  Correctly classified\\
	\midrule
	Decision Tree 	&  0.558   & 0.243   & 0.557     	& 0.558  & 0.557     & FEHLT\\
  Random Forest		&  0.556   & 0.241   & 0.562     	& 0.556  & 0.556     & FEHLT\\
  Naive Bayes		 	&  0.508   & 0.243   & 0.528     & 0.508  & 0.513 \\
  SVM							& 0.849    & 0.343   &0.842   		& 0.849  & 0.842 		 & 0.492\\
  kNN							&0.489     &0.284    &0.487     	& 0.489  & 0.488 		 & 0.489\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the contraceptive method choice dataset}
\end{table}
\bibliography{references}
